\Large Clustering Trips Identified from Automatic Number \\ Plate Recognition Camera Scans

### 2018-02-01 trips.tex
some squeezing latex

Let the $i_{th}$ sighting of vehicle \emph{k} be defined as the unordered pair:

\begin{equation} \label{e.sighting}
s^{k}_{i} = \{ c, t \},
\end{equation}

where \emph{c} uniquely identifies a camera, and \emph{t} is a scalar representing a point in time (e.g.\ a timestamp).

Let an ordered sequence of sightings of vehicle \emph{k} define the $u_{th}$ trip of vehicle \emph{k}:

\begin{equation} \label{e.trip}
w^{k}_{u} = \left(s^{k}_{(1)}, s^{k}_{(2)}, \dots , s^{k}_{(n)}\right),
\end{equation}

where \( n \) is the length of the trip, i.e.\ the number of sightings. Moreover, let the corresponding journey time sequence, of length \(n-1\), be defined as the time difference of consecutive sightings:

\begin{equation} \label{e.journeytime}
jt^{k}_{u} = \left(t^{k}_{(1)} - t^{k}_{(2)}, \ldots, t^{k}_{(n)} - t^{k}_{(n-1)} \right).
\end{equation}

We consider a trip of \emph{$w^k_u$} valid if the following conditions hold:

\begin{align}
n &\ge 1 , \label{e.trip.constraints.1} \\
\tau_{(i)} &< jt^{k}_{u(i)} < \Tau_{(i)} \ , \ \forall i \in jt^{k}_{u(i)} \label{e.trip.constraints.2},
\end{align}
{\color{blue}where $\tau$ is ... and $T_{(i)}$ ...}

>>>>

Let the $i_{th}$ sighting of vehicle \emph{k} be defined as the unordered pair:
\begin{equation} \label{e.sighting}
s^{k}_{i} = \{ c, t \},
\end{equation}
where \emph{c} uniquely identifies a camera, and \emph{t} is a scalar representing a point in time (e.g.\ a timestamp).

Let an ordered sequence of sightings of vehicle \emph{k} define the $u_{th}$ trip of vehicle \emph{k}:
\begin{equation} \label{e.trip}
w^{k}_{u} = \left(s^{k}_{(1)}, s^{k}_{(2)}, \dots , s^{k}_{(n)}\right),
\end{equation}
where \( n \) is the length of the trip, i.e.\ the number of sightings. Moreover, let the corresponding journey time sequence, of length \(n-1\), be defined as the time difference of consecutive sightings:
\begin{equation} \label{e.journeytime}
jt^{k}_{u} = \left(t^{k}_{(1)} - t^{k}_{(2)}, \ldots, t^{k}_{(n)} - t^{k}_{(n-1)} \right).
\end{equation}
We consider a trip of \emph{$w^k_u$} valid if the following conditions hold:
\begin{align}
n &\ge 1 , \label{e.trip.constraints.1} \\
\tau_{(i)} &< jt^{k}_{u(i)} < \Tau_{(i)} \ , \ \forall i \in jt^{k}_{u(i)} \label{e.trip.constraints.2},
\end{align}
{\color{blue}where $\tau$ is ... and $T_{(i)}$ ...}
